---
title: "SCORE: Fielding-Miller et al. (2020) replication"
subtitle: "Spatially correct 5% sample"
author: "Radoslaw Panczak"
date: "`r format(Sys.time(), '%d %B, %Y')`"
mainfont: DejaVu Sans
output: 
  html_document: 
    toc: true
    toc_depth: 4
    toc_float: true
    number_sections: true
    theme: united 
    highlight: pygments 
editor_options: 
  chunk_output_type: console
---

<!-- ------------------------------------------------------------ --> 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      fig.width=8, fig.height=6, dpi=300, 
                      out.width="800px", out.height="600px")

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

options(scipen=999)

set.seed(12345)

library(pacman) 

p_load(tidyverse, sf, tmap, scales,
       igraph, spdep)

tmap_mode("view")
```


# County boundaries

Using `20m` (most generlized) file.

```{r load, include=FALSE}
counties_raw <- st_read("data-raw/Raw files/Spatial/cb_2018_us_county_20m/cb_2018_us_county_20m.shp") %>% 
  select(-ALAND, -AWATER)
```


```{r}
# qtm(counties_raw)
# View(st_drop_geometry(counties_raw))
```

Excluding Hawaii: 

```{r}
counties_raw %>% 
  filter(STATEFP == 15) %>% 
  qtm(fill = "purple", borders = NULL)
```

Excluding Puerto Rico: 

```{r}
counties_raw %>% 
  filter(STATEFP >= 60) %>% 
  qtm(fill = "purple", borders = NULL)
```

```{r include=FALSE}
counties <- counties_raw %>% 
  filter(STATEFP != 15) %>% 
  filter(STATEFP < 60)

# saving prep file for Stata
counties %>% 
  mutate(fips = as.integer(GEOID)) %>% 
  rename(state_code = STATEFP) %>% 
  select(fips, state_code) %>% 
  st_write("data/cb_2018_us_county_20m_prep.shp", delete_dsn = TRUE)
```

Final dataset used:

```{r}
qtm(counties, borders = "purple", fill = NULL)
```

From these set of `r nrow(counties)` counties 5% sample would mean `r round(nrow(counties)*0.05)` polygons.

Also - important to notice - there are two counties with no neighbours

```{r}
counties %>% 
  slice(2463) %>% 
  qtm(borders = "purple", text= "NAME", text.col = "purple", fill = NULL)
```


```{r}
counties %>% 
  slice(2727) %>% 
  qtm(borders = "purple", text= "NAME", text.col = "purple", fill = NULL)
```

And also important to notice the text from the paper:

>  Within this dataset, the 5 boroughs/counties of New York are treated as a single entity.
We have done the same in these analyses, assigning all 5 counties the values
associated with New York County

The counties in question are most likely these

  - The Bronx is Bronx County (FIPS 36005)
  - Brooklyn is Kings County (FIPS 36047)
  - Manhattan is New York County (FIPS 36061)
  - Queens is Queens County (FIPS 36081)
  - Staten Island is Richmond County (FIPS 36085)
  
```{r}
counties_raw %>% 
  filter(GEOID %in% c(36005, 36047, 36061, 36081, 36085)) %>% 
  qtm(borders = "purple", fill = NULL)
```

**At the moment, using dataset prepared these counties are excluded from analyses since there is no merge to explanatory variables and no spatial join possible!**

# Solution 1: picking one state at random

Might be an option. Must be the same in between runs? Most likely not enough counties?

```{r}
length(unique(counties$STATEFP))
selected <- sample(unique(counties$STATEFP), 1)

selected

counties %>% 
  filter(STATEFP == selected) %>% 
  select(NAME) %>% 
  nrow()

counties %>% 
  filter(STATEFP == selected) %>% 
  qtm(borders = "purple", fill = NULL)
```


# Solution 2: picking fixed state 

```{r}
selected <- 48
```

Texas as the biggest state that gives `r round((nrow(counties[counties$STATEFP == selected,])/nrow(counties))*100, digits = 1)` data?

```{r}
counties %>% 
  filter(STATEFP == selected) %>% 
  select(NAME) %>% 
  nrow()

counties %>% 
  filter(STATEFP == selected) %>% 
  qtm(borders = "purple", fill = NULL)
```

# Solution 3: `st_sample` 

Unfortunately non contiguous :/

```{r}
sample <- st_sample(counties, 
                    size = round(nrow(counties)*0.05), 
                    type = "random") 

sample %>% 
  qtm()

st_join(counties, st_sf(sample), join = st_intersects, left = FALSE) %>% 
  qtm(borders = "purple", fill = NULL)
```

# Solution 4: `igraph`, `spdep` and `sf` custom solution

Solution suggested by @Spacedman [here](https://gis.stackexchange.com/questions/375177/in-r-how-do-i-generate-r-random-sample-of-contiguous-polygons).

```{r}
connectUp <- function(polys, n){
    nb = spdep::poly2nb(polys)
    g = igraph::graph.adjlist(nb)

    selected = sample(nrow(polys),1)

    while(length(selected) < n){
        nbrs = unlist(igraph::ego(g, 1, selected, mindist=1))
        newnbrs = setdiff(nbrs, selected)
        selected = c(selected, sample(newnbrs,1))
    }
    return(selected)
}

temp <- counties %>% 
  slice(-c(2463, 2727))

connected <- connectUp(temp, round(nrow(temp)*0.05))

temp[connected, ] %>% 
  qtm(borders = "purple", fill = NULL)

temp[connected, ] %>% 
  mutate(fips = as.integer(GEOID)) %>% 
  rename(state_code = STATEFP) %>% 
  select(fips, state_code) %>% 
  st_write("data/cb_2018_us_county_20m_prep_sample.shp", delete_dsn = TRUE)

temp[connected, ] %>% 
  mutate(fips = as.integer(GEOID)) %>% 
  select(fips) %>% 
  st_drop_geometry() %>% 
  st_write("data/fips_sample.shp", delete_dsn = TRUE)
```

**These are counties that will be used as input for 5% sample analyses!**
