---
title: "SCORE: Fielding-Miller et al. (2020) replication"
subtitle: "Spatially correct 5% sample"
author: "Radoslaw Panczak"
date: "`r format(Sys.time(), '%d %B, %Y')`"
mainfont: DejaVu Sans
output: 
  html_document: 
    toc: true
    toc_depth: 4
    toc_float: true
    number_sections: true
    theme: united 
    highlight: pygments 
editor_options: 
  chunk_output_type: console
---

<!-- ------------------------------------------------------------ --> 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      fig.width=8, fig.height=6, dpi=300, 
                      out.width="800px", out.height="600px")

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

options(scipen=999)

set.seed(12345)

library(pacman) 

p_load(tidyverse, sf, tmap, scales)

tmap_mode("view")
```


# County boundaries

```{r load, include=FALSE}
counties_raw <- st_read("data-raw/Spatial/cb_2018_us_county_20m/cb_2018_us_county_20m.shp") %>% 
  select(-ALAND, -AWATER)

qtm(counties_raw)
View(st_drop_geometry(counties_raw))

# to exclude
counties_raw %>% 
  filter(STATEFP == 15 | STATEFP >= 60) %>% 
  qtm(fill = "purple", borders = NULL)

counties <- counties_raw %>% 
  filter(STATEFP != 15) %>% 
  filter(STATEFP < 60)
```

Excluding Hawaii & Puerto Rico

```{r}
qtm(counties, borders = "purple", fill = NULL)
```

We have `r nrow(counties)` counties and 5% sample would mean `r round(nrow(counties)*0.05)` polygons.

```{r load, include=FALSE}
counties %>% 
  mutate(fips = as.integer(GEOID)) %>% 
  rename(state_code = STATEFP) %>% 
  select(fips, state_code) %>% 
  st_write("data/cb_2018_us_county_20m_prep.shp", delete_dsn = TRUE)
```


# Picking one state at random

Might be an option. Must be the same in between runs? Most likely not enough counties?

```{r}
length(unique(counties$STATEFP))
selected <- sample(unique(counties$STATEFP), 1)

selected

counties %>% 
  filter(STATEFP == selected) %>% 
  select(NAME) %>% 
  nrow()

counties %>% 
  filter(STATEFP == selected) %>% 
  qtm(borders = "purple", fill = NULL)
```


# Picking fixed state 

```{r}
selected <- 48
```

Texas as the biggest state that gives `r round((nrow(counties[counties$STATEFP == selected,])/nrow(counties))*100, digits = 1)` data?

```{r}
# selected

counties %>% 
  filter(STATEFP == selected) %>% 
  select(NAME) %>% 
  nrow()

counties %>% 
  filter(STATEFP == selected) %>% 
  qtm(borders = "purple", fill = NULL)
```

# `st_sample` 

Unfortunately non contiguous :/

```{r}
sample <- st_sample(counties, 
                    size = round(nrow(counties)*0.05), 
                    type = "random") 

sample %>% 
  qtm()

st_join(counties, st_sf(sample), join = st_intersects, left = FALSE) %>% 
  qtm(borders = "purple", fill = NULL)
```

